Next Trippy Structures\thanks{Supported by organization x.}

### 2019-02-21 paper.tex
Size tables

\usepackage{enumerate}
\usepackage{marginnote}
\usepackage[linesnumbered,commentsnumbered,boxed]{algorithm2e}
\usepackage{amsmath}
\usepackage{threeparttable}

@@

\subsection{CTR version de spire...}
y despues la variante nueva (CTR2M).

@@

\begin{threeparttable}
\caption{Efficiency of \acumm~and \ctr~against the queries described in Section~\ref{sec:rq}}
\label{tab:queries}
\begin{tabular}{|l|l|l|}
\hline
Query &  \acumm & \ctr\\
\hline
\texttt{board\_X$_{LT}$} & $O(l)$\tnote{a} & \ctrq\tnote{b} \\
\texttt{alight\_X$_{LT}$} & $O(l)$\tnote{a} & Hard\tnote{cd} \\
\texttt{start\_X$_{LT}$} & - & \ctrq\tnote{b} \\
\texttt{end\_X$_{LT}$} & - & \ctrq\tnote{b} \\
\texttt{switch\_X$_{LT}$} & - & \ctrq\tnote{b} \\
\texttt{from\_X$_{LT}$\_to\_Y$_{LT}$} & - & \ctrq\tnote{b} \\
\texttt{board\_L$_T$} & O(1) & $O(|S| \times \ctrq)$\tnote{be} \\
\texttt{alight\_L$_T$} & O(1) & $O(|S| \times \ctrq)$\tnote{bce} \\
\texttt{start\_L$_T$} & - & $O(log(|L|\times\bar{|J^l|}))$\tnote{fg} \\
\texttt{end\_L$_T$} & - & $O(|S| \times \ctrq)$\tnote{be} \\
\texttt{board\_T} & $O(|L|)$\tnote{f} & Hard\tnote{d} \\
\texttt{alight\_T} & $O(|L|)$\tnote{f} & Hard\tnote{cd} \\
\texttt{start\_T} & - & $O(|L| \times log(|L|\times\bar{|J^l|}))$\tnote{fg} \\
\texttt{end\_T} & - & Hard\tnote{d} \\
\texttt{load\_X$_{LT}$} & $O(l)$\tnote{a} & Hard\tnote{cd} \\
\hline
\end{tabular}

@@

\subsection{Space requirments}
Missing space tables with total size, compression and bps!

\subsection{Query performance}
Missing a comparison of \acumm vs \ttctr!

>>>>

\usepackage{enumerate}
\usepackage{marginnote}
\usepackage[linesnumbered,commentsnumbered,boxed]{algorithm2e}
\usepackage{amsmath}
\usepackage{threeparttable}
\usepackage[margin=0pt,skip=1pt]{subcaption}

@@

\subsection{\ttctr}
Version de spire y despues la variante nueva (\ctr).

@@

\begin{threeparttable}
\centering
\caption{Efficiency of \acumm~and \ctr~against the queries described in Section~\ref{sec:rq}}
\label{tab:queries}
\begin{tabular}{|l|l|l|}
\hline
Query &  \acumm & \ctr\\
\hline
\texttt{board\_X$_{LT}$} & $O(l)$\tnote{a} & \ctrq\tnote{b} \\
\texttt{alight\_X$_{LT}$} & $O(l)$\tnote{a} & Hard\tnote{cd} \\
\texttt{start\_X$_{LT}$} & - & \ctrq\tnote{b} \\
\texttt{end\_X$_{LT}$} & - & \ctrq\tnote{b} \\
\texttt{switch\_X$_{LT}$} & - & \ctrq\tnote{b} \\
\texttt{from\_X$_{LT}$\_to\_Y$_{LT}$} & - & \ctrq\tnote{b} \\
\texttt{board\_L$_T$} & O(1) & $O(|S| \times \ctrq)$\tnote{be} \\
\texttt{alight\_L$_T$} & O(1) & $O(|S| \times \ctrq)$\tnote{bce} \\
\texttt{start\_L$_T$} & - & $O(log(|L|\times\bar{|J^l|}))$\tnote{fg} \\
\texttt{end\_L$_T$} & - & $O(|S| \times \ctrq)$\tnote{be} \\
\texttt{board\_T} & $O(|L|)$\tnote{f} & Hard\tnote{d} \\
\texttt{alight\_T} & $O(|L|)$\tnote{f} & Hard\tnote{cd} \\
\texttt{start\_T} & - & $O(|L| \times log(|L|\times\bar{|J^l|}))$\tnote{fg} \\
\texttt{end\_T} & - & Hard\tnote{d} \\
\texttt{load\_X$_{LT}$} & $O(l)$\tnote{a} & Hard\tnote{cd} \\
\hline
\end{tabular}

@@

\subsection{Space requirments}
Discuss why we are getting these sizes, and compare. Missing \acumm~sizes!

\begin{table}
    \centering
    \caption{Sizes of the common structures}
    \begin{tabular}{|c|c|c|c|c|c|}
    \hline
        Structure & $lineStop$ & $stopLine$ & $avgTime$ & $initialTime$ & Total \\
        \hline
        Size (KiB) & 119 & 141 & 64 & 440 & 764 \\
    \hline
    \end{tabular}
\end{table}

\begin{table}
    \caption{Space requirements for the CSA (a) and the WM (b) from \ttctr}
    \begin{subtable}[t]{.48\linewidth}
    \vspace{-12pt}
    \caption{\footnotesize (a)}
    \vspace{-12pt}
    \begin{tabular}[t]{|l|l|r|r|}
        \hline
        Param. & bps & Size (MiB) & Comp. (\%) \\
         \hline
        baseline & 16 & 67.85 & 100.00 \\
        32 & 7.288 & 30.91 & 45.55 \\
        128 & 6.069 & 25.74 & 37.93 \\
        512 & 5.761 & 24.43 & 36.01 \\
        \hline
    \end{tabular}
    \end{subtable}%
    \begin{subtable}[t]{.48\linewidth}
    \vspace{-12pt}
    \caption{\footnotesize (b)}
    \vspace{-12pt}
    \begin{tabular}[t]{|l|l|r|r|}
        \hline
        Param. & bps & Size (MiB) & Comp. (\%) \\
         \hline
        baseline & 14 & 42.68 & 100.00 \\
        RG32 & 14.438 & 44.02 & 103.13 \\
        RG32 & 13.478 & 41.09 & 96.27 \\
        RG64 & 12.79 & 38.99 & 91.36 \\
        RG128 & 12.446 & 37.94 & 88.90 \\
        \hline
    \end{tabular}
    \end{subtable}
\end{table}

\begin{table}
    \caption{Space requirements for the CSA (a), the WMJ (b) and the WML (c) from \ctr}
    \begin{subtable}[t]{.48\linewidth}
    \vspace{-12pt}
    \caption{\footnotesize (a)}
    \vspace{-12pt}
    \begin{tabular}[t]{|l|l|r|r|}
        \hline
        Param. & bps & Size (MiB) & Comp. (\%) \\
         \hline
        baseline & 14 & 59.37 & 100.00 \\
        32 & 6.956 & 29.50 & 49.69 \\
        128 & 5.727 & 24.29 & 40.91 \\
        512 & 5.417 & 22.97 & 38.69 \\
        \hline
    \end{tabular}
    \end{subtable}
    \begin{subtable}[t]{.48\linewidth}
    \vspace{-12pt}
    \caption{\footnotesize (b)}
    \vspace{-12pt}
    \begin{tabular}[t]{|l|l|r|r|}
        \hline
        Param. & bps & Size (MiB) & Comp. (\%) \\
         \hline
        baseline & 14 & 59.37 & 100.00 \\
        RG32 & 14.438 & 61.23 & 103.13 \\
        RG32 & 13.419 & 56.91 & 95.85 \\
        RG64 & 12.732 & 53.99 & 90.94 \\
        RG128 & 12.388 & 52.53 & 88.49 \\
        \hline
    \end{tabular}
    \end{subtable}
    \begin{subtable}[t]{.48\linewidth}
    \vspace{-12pt}
    \caption{\footnotesize (c)}
    \vspace{-12pt}
    \begin{tabular}[t]{|l|l|r|r|}
        \hline
        Param. & bps & Size (MiB) & Comp. (\%) \\
         \hline
        baseline & 14 & 59.37 & 100.00 \\
        RG32 & 14.438 & 61.23 & 103.13 \\
        RG32 & 13.419 & 56.91 & 95.85 \\
        RG64 & 12.732 & 53.99 & 90.94 \\
        RG128 & 12.388 & 52.53 & 88.49 \\
        \hline
    \end{tabular}
    \end{subtable}%
\end{table}

\subsection{Query performance}
Missing a comparison of \acumm~vs \ttctr!
